Predicting Levels of Sales for Newly Published Books \\ using Cost-Sensitive Ensemble Methods

### 2016-12-05 paper.tex
adding contents to INTRODUCTION

Determining the number of copies of a new book should the publisher print, the 
so called {\em print run}, for delivery to bookstores is a challenging problem.
Thus, it is extremely important to develop an accurate predictive method which 
could forecast the future sales a new book will achieve, in order to optimise 
production schedules, improve the publishing company profits and minimise 
losses \cite{Zhao2001}.

@@

@@

To make the print run as close as possible to the actual level of sales, it is 
essential to have an estimation of those sales.
In this sense, this paper continues our previous work on book sales prediction 
\cite{Castillo2016books} in which the main factors influencing sales where 
analyzed in order to create a tool that the publisher can use to decide how many 
books should be printed.

In this paper, the challenge we are taking is determining the actual level of 
sales a new book will achieve.

>>>>

Determining the number of copies of a new book should the publisher print, the 
so called {\em print run}, for delivery to bookstores is a challenging problem.

Thus, it is extremely important to develop accurate predictive methods which 
could forecast the future sales a new book will achieve, in order to optimise 
production schedules, improve the publishing company profits and minimise 
losses \cite{Zhao2001}.

@@

Usually the methods used to predict book sales have
been generally based on experts' experience, who analyse data about sales and, 
taking into account their knowledge of the industry, their experience, and their 
perception about trends, could make decisions on the companies production.
However, this process might be tedious, especially when the amount of data is 
quite large. Moreover, different experts can reach different predictions from 
the same dataset \cite{Sanders1994}.

@@

To make the print run as close as possible to the actual level of sales, it is 
essential to have an estimation of those sales. 
In this sense, this paper continues our previous work on book sales prediction 
\cite{Castillo2016books} in which the main factors influencing sales where 
analyzed in order to create a tool that the publisher can use to decide how many 
books should be printed.
In that paper, several regression methods were applied to estimate sales for new launched books using a real dataset of book sales related to the Spanish market, provided by the Spanish publishing company Trevenque Editorial S.L.\footnote{{\tt http://editorial.trevenque.es}

However, as finding adequate forecasting techniques and selecting the best method 
to use represent also a problem, we propose configuring complex models based on
ensembles \cite{Qiu2014} in order to face the challenge of determining the actual 
level of sales a new book will achieve.
Moreover, since publishers need models to explain obtained predictions, and 
`black box' forecasting methods may not be suitable, using these ensemble 
models publishers will be able to combine their expert knowledge about the 
market with the created forecasting models in order to get a reliable estimation 
of book sales level.
